The Spatial Distribution of Local Group Satellites in a Cosmological Context

### 2016-06-13 paper/ms.tex
mas referencias

\subsection{Problemas con esas explicaciones:}
The Vast Polar Structure of the Milky Way and Filamentary Accretion of
Sub-Halos (Pawlowski et al 2012)\\
Paper de Collins (2013 y 2016) donde explica que no hay doferencias en
las propiedades de los on-plane y los off-plane satellites\\
Problemas con la estabilidad a largo plazo de los planos: Bowden et al
2012, Gonzales et al 2015...\\
The Plane Truth: Andromeda analog thin Planes of Satellites are not
kinematical coherent structures (Buck et al 2015)\\

@@

\citep{2015MNRAS.450.2727T} They measure the angle between satellites
and the direction defined by filaments (Bissous filament finder )to
find a signal both in SDSS and the semi-analytic galaxies in the
Millennium Simulation.

@@

\citep{2016MNRAS.457.1931S} Uses the APOSTLE simulation (12 pairs) to study the
spatial anisotropy the 11 brightest satellites. THe anisotropy is
quantified the reduced inertia tensor. Still the MW is more
anisotropic than all but one of the 24 halos. The analysis is not very
thorough and do not show the resulting distribution. Does not compare
the results of using DM information only.

@@

\end{itemize}

>>>>

\subsection{Problemas con esas explicaciones:}
The Vast Polar Structure of the Milky Way and Filamentary Accretion of
Sub-Halos (Pawlowski et al 2012)\\
Paper de Collins (2013 y 2016) donde explica que no hay diferencias en
las propiedades de los on-plane y los off-plane satellites\\
Problemas con la estabilidad a largo plazo de los planos: Bowden et al
2012, Gonzales et al 2015...\\
The Plane Truth: Andromeda analog thin Planes of Satellites are not
kinematical coherent structures (Buck et al 2015)\\

@@

\citep{2015MNRAS.450.2727T} They measure the angle between satellites
and the direction defined by filaments (Bissous filament finder) to
find a signal both in SDSS and the semi-analytic galaxies in the
Millennium Simulation.

@@

\citep{2016MNRAS.457.1931S} Uses the APOSTLE simulation (12 pairs) to study the
spatial anisotropy the 11 brightest satellites. The anisotropy is
quantified the reduced inertia tensor. Still the MW is more
anisotropic than all but one of the 24 halos. The analysis is not very
thorough and do not show the resulting distribution. Does not compare
the results of using DM information only.

@@

\item{Sawala et al. 2014 "The chosen few: the low mass halos that host faint galaxies":\\
Conclusion: Some "effects make dwarf galaxies highly biased
tracers of the underlying dark matter distribution."\\
Simulation: 12 cosmological volumes as zoom" simulations
extracted from the Dove simulation. They require that each box has to
have two halos (MW and M31 like)\\
Gas: Yes (they also compare their results with DM only simulations)\\
Resolution : sub-halos 1 $\times 10^7 M\odot$\\
Number of host halos:  2 times 12 (pairs of galaxies).\\
Planes: They do not look for them\\}

\item{Libeskind et al. 2012 "The universal nature of subhalo accretion":\\
Conclusion: "the preferential infall of subhaloes is effectively universal
in the sense that its always aligned with the axis of weakest collapse
of the velocity shear tensor. It is the same shear tensor that
dictates the structure of the cosmic web and hence the shear field
emerges as the key factor that governs the local anisotropic pattern
of structure formation."\\
Simulation:DM-only N-body simulation of 10243 particles in a
64h$^{-1}$ Mpc box.\\
Gas: NO\\
Resolution : particle 1.89 $\times 10^7 h^{-1} M\odot$\\
Resolution : halos 1$\times 10^9 h^{-1} M\odot$\\
Number of host halos:  not mentioned.\\
Planes: They do not look for them. They look and find preferential
directions for accretion\\}

\item{Libeskind et al. 2015 "Planes of satellite galaxies and the
cosmic web":\\
Conclusion:"The analysis reveals that the Local Group and Centaurus A
reside in a filament stretched by the Virgo cluster and compressed by
the expansion of the Local Void. Four out of five thin planes of
satellite galaxies are indeed closely aligned with the axis of
compression induced by the Local Void. (...) "\\ 
Simulation: Observational paper uses the cosmic flow data set.\\
Gas: No aplica\\
\\}

\item{Tempel et al. 2015 "The alignment of satellite galaxies and
cosmic filaments: observations and simulations":\\
Conclusion:"A statistically significant alignment between satellite
galaxy position and filament axis in observations is confirmed. We
find a qualitatively compatible alignments by examining satellites and
filaments similarly identified in the Millennium simulation,
semi-analytical galaxy catalogue. We also examine the dependence of
the alignment strength on galaxy properties such as colour, magnitude
and (relative) satellite magnitude, finding that the alignment is
strongest for the reddest and brightest central and satellite
galaxies. "\\ 
Simulation: MilleniumII compared to Observational data (SDSS).\\
Gas: No\\
Alignments: yes both in simulations and in observations\\
Note: they make a statistical analysis of alignments in projected
data.}

\item{Sawala et al. 2015 "The APOSTLE simulations: solutions to the
Local Group's cosmic puzzles":\\
Conclusion: "Applying the Eagle code to the LG environment, we find
that our simulations match the observed abundance of LG galaxies,
including the satellite galaxies of the MW and Andromeda. Due to
changes to the structure of halos and the evolution in the LG
environment, the simulations reproduce the observed relation between
stellar mass and velocity dispersion of individual dwarf spheroidal
galaxies without necessitating the formation of cores in their dark
matter profiles. Satellite systems form with a range of spatial
anisotropies, including one similar to that of the MW, confirming that
such a configuration is not unexpected in $\Lambda$CDM"\\ 
Simulation: They use the EAGLE code to simulate the Apostole set of
simulations (a suite of cosmological hydro-
dynamic simulations of twelve volumes selected to match the kinematics
of the Local Group (LG) members).\\
halo selection:In particular, we focus
on pairs of halos that match the separation, approach
velocity, and relative tangential velocity of the Milky Way
(MW) and Andromeda (M31). From a large cosmological
simulation, we have selected twelve pairs of halos with combined
virial masses of  2.3$\pm$0.6$\times 10^{12}M_\odot$, compatible
with the most recent dynamical constraints\\ 
Resolution : re-simulated each LG volume at several resolutions,
both as dark matter only (DMO) simulations, and
as hydrodynamic simulations\\
Gas: Yes (they also compare with DM only simulations)\\
planes: yes (they find "anisotropic configurations: BUT not typical ")\\
Note: they select MW-M31-like pairs, including kinematical
constraints\\}

\item{ Gillet et al. 2015: "Vast planes of satellites in a high resolution simulation of
the Local Group: comparison to Andromeda":\\
CLUES project and a semi-analytic model\\
Conclusion: "The structure of the simulated satellite systems is
strongly non-random and contains planes of satellites, predominantly
co-rotating, with, in some cases, sizes comparable to the plane
observed in M31 by Ibata et al.. However the latter is slightly richer
in satellites, slightly thinner and has stronger co-rotation, which
makes it stand out as overall more exceptional than the simulated
planes, when compared to a random population" \\
Simulation: CLUES\\
Gas: NO\\
Resolution : DM particle 2.1 $\times 10^5 h^{-1} M\odot$\\
Resolution : gas particle 4.42 $\times 10^4 h^{-1} M\odot$\\
Resolution : halos $4.2\times 10^6 h^{-1} M\odot$\\
Number of host halos: 2 (one pair)\\
Planes: yes\\
co-rotation: kind of\\
Stable: No\\
note: they use 5 different methods to choose the satellites and 3
different volumes.\\
}

\item{ Pawlowski et al. 2012: "Can filamentary accretion explain the
orbital poles of the Milky Way satellites?":\\
Aquarius and Via Lactea Simulations\\
Conclusion: they find that the simulations cannot reproduce the
angular momentum coherence of the satellites in the MW and that "this
indicates that the formation as tidal dwarf galaxies in a single
encounter is a viable, if not the only, process to explain the
phase-space distribution of the MW satellite galaxies." \\
Simulation: Aquarius and Via Lactea\\
Gas: NO\\
Resolution : ?\\
Number of host halos: 8\\
Planes: they look for alignments in the orbital poles and found none
in the cosmological simulations\\
co-rotation: no\\
note: they compare what they find in simulations with an isotropic
distribution and with merger scenarios.\\
}

\item{ Pawlowski et al. 2014: "Co-orbiting planes of sub-halos are
similarly unlikely around paired and isolated hosts":\\
They use the Elvis simulations to study the satellite population of
paired vs isolated galaxies.\\
Conclusion: The observed flattening and the observed orbital alignment
are each reproduced by only 0.2 to 2 per cent of paired and isolated
systems incorporating the obscuration of satellites by randomly
oriented galactic discs.\\
Simulation: Elvis\\
Gas: NO\\
Resolution : ?\\
Number of host halos: 24 paired and 24 isolated host halos (4800
analyzed realizations).\\
Planes: 0.2 to 2 per cent\\
co-rotation: 0.2 to 2 per cent\\
note: co-rotation and alignments together are only observed in ONE of
4800 realizations.\\
}
\end{itemize}
